Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
Modify Sect 6

The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \citep{Azzalini1985}. The SN distribution has, in addition to a location and a scale parameter analogous to the Normal distribution's mean and standard deviation, a third parameter which describes the skewness (i.e. the asymmetry) of the distribution. Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $y\in Y$ can be written as 
\begin{equation} \label{def:snd_gen}
SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right),
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution\footnote{A standard Normal distribution is a Normal distribution with a mean of 0 and a standard deviation of 1.}.
The skewness parameter $\alpha$ quantifies the asymmetry of the SN. 
Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Fig.~\ref{fig:SN.plot}.  A usual Normal distribution is the special case of the SN distribution when the skewness parameter $\alpha$ is equal to zero\footnote{This can be seen from Eq.~\ref{def:snd_gen}. If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0) = 0.5$ and therefore $SN(y;\xi, \omega, 0) = \frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$ which is the density of a Normal distribution. Note that $\Phi(0) = 0.5$ because $\Phi(0)$ is the the probability that a standard Normal random variable is less than or equal than 0.}.
%
\begin{figure}[htbp]
\begin{center}
\includegraphics[height = 3in]{Skew_Normal_densities_jjck.pdf} 
   \caption{Density function of a random variable Y following the SN distribution $SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types. Note that the solid black line has an $\alpha = 0$, making it a Normal distribution.}
   \label{fig:SN.plot}
\end{center}
\end{figure}
%
For reasons related to the interpretation of the parameters in Eq.~\ref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used in this work, which is referred to as the \emph{centered parametrization} (CP).  This CP is much closer to the parametrization of a Normal distribution, as it uses a mean parameter $\mu$, a variance parameter $\sigma^2$ and a skewness parameter $\gamma$. In order to define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of $(\xi, \omega^2, \alpha)$. This can be done using the following relations:
%
\begin{equation} \label{eq:snd_cp}
\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2},
\end{equation}
%
where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$ \citep[e.g.][]{Arellano-2010}.

@@

Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a faculae, \xavier{we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its efficiency in the case of a faculae.} The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}. 
It is straightforward to see that the proposed correction for \xavier{stellar activity is able to account for the majority of the activity signal created by a faculae, with a $R^2$ of our model larger than 0.95. In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correction to values below 0.15 \ms after correction.
We see a slightly smaller rms after correction for the SN parameters, however the different is not significant. When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used, i.e. a linear combination of the asymmetry and width parameter, we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2. Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the intercept $\beta_0$ is only significant at a level of 1\% in the case of the Normal parameters, the coefficient $\beta_3$ that corresponds to the CCF width is only significant when using the SN parameters, and the coefficient $\beta_4$ that account for the interaction between the width and the asymmetry parameters is never significant.}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity the residuals do not show a systematic component.}
    \label{fig:faculae.correction}
\end{center}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.0016$    & $0.26$ & $0.60$ \\
\hline
$\beta_{1}$            &    $3.75e-05$    & $0.0068$ & $0.0069$ \\
\hline
$\beta_{2}$            &     $7.79e-16$   &  $1.97e-05$ & $3.69e-08$\\
\hline
$\beta_{3}$            &     $0.25$   &  $0.0011$ & $0.0011$\\
\hline
$\beta_{4}$            &     $0.53$   &  $0.21$ & $0.21$\\
\hline
$R^{2}$      &     $0.9967$    &  $0.9571$ & $0.977$  \\
\hline
\end{tabular}
\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a faculae, according to Eq.~\ref{eq:RV:correction}. Beyond the contrast parameter A and the asymmetry parameter of the CCF which are useful for both the analyses, the width of the CCF is statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses. The term of interaction between the asymmetry and the width of the CCF is not helpful to explain part of the variability in the set of RV's. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
\label{table:faculae.test}
\end{table}

@@

As before, we corrected the originally RVs by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction}. Also in this case the proposed correction almost completely addresses the issue when considering the SN or Normal parameters, with values of $R^2$ larger than 0.98. \xavier{Looking at Fig.~\ref{fig:spot.correction}, we see that the activity correction proposed here is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms. In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however,} \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant. When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.

In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summmurized in Table \ref{table:spot.test}, we observe that the intercept and $\beta_3$, corresponding to the width of the CCF, are useless to understand the variation seen in RVs. This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}. We see also that the ampltitude parameter, with coefficient $\beta_1$ is only useful to explain the RV variation of the spot in the case of the Normal distribution.}

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity the residuals do not show a systematic component.}
    \label{fig:spot.correction}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.47$    & $0.84$ & $0.81$ \\
\hline
$\beta_{1}$            &    $0.00035$    & $0.064$ & $0.064$ \\
\hline
$\beta_{2}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
$\beta_{3}$            &     $0.53$   &  $0.61$ & $0.61$\\
\hline
$\beta_{4}$            &     $1.11e-07 $   &  $2.85e-08 $ & $ 2.87e-08 $\\
\hline
$R^{2}$      &     $0.9897$    &  $0.9914$ & $0.9929$  \\
\hline
\end{tabular}
\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\ref{eq:RV:correction}. All the covariates are statistically useful to explain the variability in RV's causued by a spot except the intercept and the width of the CCF. Concerning the SN analysis, the contrast parameter A is not statistically significant at level $5\%$. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
\label{table:spot.test}
\end{table}

@@

%HD192310
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}192310$. The last three plots show the correlation between the FWHM and the RV's for $\text{HD}192310$ using respectively the SN and the Normal fits. The p--values associated with each $R$ is statistically different from $0$.}
   \label{fig:Gliese785:corrPlot}
\end{figure*}

\begin{figure*} 
   \centering
\includegraphics[height = 6in]{NEW_CORRECTIONHD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of RV's for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq. \ref{eq:RV:correction}. Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
   \label{fig:HD192310:correctionRV}
\end{figure*}

%HD10700
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}10700$. The last three plots show the correlation between the FWHM and the RV's for $\text{HD}10700$ using respectively the SN and the Normal fits. The p--values associated with each $R$ is statistically different from $0$.}
   \label{fig:Tau:corrPlot}
\end{figure*}

\begin{figure*} 
   \centering
\includegraphics[height = 6in]{NEW_CORRECTIONHD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of RV's for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq. \ref{eq:RV:correction}. Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
   \label{fig:HD10700:correctionRV}
\end{figure*}

%HD215152
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}215152$. The last three plots show the correlation between the FWHM and the RV's for $\text{HD}215152$ using respectively the SN and the Normal fits. Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
   \label{fig:HD215152:corrPlot}
\end{figure*}

\begin{figure*} 
   \centering
\includegraphics[height = 6in]{NEW_CORRECTIONHD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of RV's for $\text{HD}215152$ using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq. \ref{eq:RV:correction}. Once corrected for stellar activity, the residuals for the Normal are $0.054$ \ms higher than the residuals retrieved with the SN analysis.}
   \label{fig:HD215152:correctionRV}
\end{figure*}

%Corot-7
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
   \caption{Correlation between the asymmetry parameters and the RV's for  $\text{Corot }7$. The last three plots show the correlation between the FWHM and the RV's for  $\text{Corot }7$ using respectively the SN and the Normal fits. Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
   \label{fig:Corot7:corrPlot}
\end{figure*}

\begin{figure*} 
   \centering
\includegraphics[height = 6in]{NEW_CORRECTIONLRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of RV's for  $\text{Corot }7$ using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq. \ref{eq:RV:correction}. Once corrected for stellar activity, the residuals for the Normal are $0.336$ \ms higher than the residuals retrieved with the SN analysis.}
   \label{fig:Corot-7:correctionRV}
\end{figure*}

>>>>

The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \citep{Azzalini1985}. The SN distribution has, in addition to a location and a scale parameter analogous to the Normal distribution's mean and standard deviation, a third parameter which describes the skewness (i.e. the asymmetry) of the distribution. Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $y\in Y$ can be written as 
\begin{equation} \label{def:snd_gen}
SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right),
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution\footnote{A standard Normal distribution is a Normal distribution with a mean of 0 and a standard deviation of 1.}.
The skewness parameter $\alpha$ quantifies the asymmetry of the SN. 
Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Fig.~\ref{fig:SN.plot}.  A usual Normal distribution is the special case of the SN distribution when the skewness parameter $\alpha$ is equal to zero\footnote{This can be seen from Eq.~\ref{def:snd_gen}. If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0) = 0.5$ and therefore $SN(y;\xi, \omega, 0) = \frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$ which is the density of a Normal distribution. Note that $\Phi(0) = 0.5$ because $\Phi(0)$ is the the probability that a standard Normal random variable is less than or equal than 0.}.
%
\begin{figure}[htbp]
\begin{center}
\includegraphics[height = 2.3in]{Skew_Normal_densities_jjck.pdf} 
   \caption{Density function of a random variable Y following the SN distribution $SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types. Note that the solid black line has an $\alpha = 0$, making it a Normal distribution.}
   \label{fig:SN.plot}
\end{center}
\end{figure}
%
For reasons related to the interpretation of the parameters in Eq.~\ref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used in this work, which is referred to as the \emph{centered parametrization} (CP).  This CP is much closer to the parametrization of a Normal distribution, as it uses a mean parameter $\mu$, a variance parameter $\sigma^2$ and a skewness parameter $\gamma$. In order to define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of $(\xi, \omega^2, \alpha)$. This can be done using the following relations:
%
\begin{equation} \label{eq:snd_cp}
\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2},
\end{equation}
%
where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$ \citep[e.g.][]{Arellano-2010}.

@@

Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a faculae, \xavier{we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its efficiency in the case of a faculae.} The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}. 
It is straightforward to see that the proposed correction for \xavier{stellar activity is able to account for the majority of the activity signal created by a faculae, with a $R^2$ of our model larger than 0.95. In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correction to values below 0.15 \ms after correction.
We see a slightly smaller rms after correction for the SN parameters, however the different is not significant. When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used, i.e. a linear combination of the asymmetry and width parameter, we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2. Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the \umberto{parameter related to the} intercept, $\beta_0$, is only significant at a level of 1\% in the case of the Normal parameters \umberto{or when SN median RV is used}.}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{\umberto{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity. The new correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity using the proposed linear function (black dots), the residuals present a smaller systematic component if compared with the residuals obtained with the usual correction (blue triangles).}}
    \label{fig:faculae.correction}
\end{center}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.033$    & $0.00020$ & $0.61$ \\
\hline
$\beta_{1}$            &    $2.22e-16 $    & $2.22e-16 $ & $2.22e-16 $ \\
\hline
$\beta_{2}$            &     $0.0034$   &  $2.22e-16 $ & $2.22e-16 $\\
\hline
$\beta_{3}$            &     $0.00016$   &  $1.091e-6$ & $9.75e-7$\\
\hline
$\beta_{4}$            &     $2.22e-16$   &  $2.22e-16$ & $2.22e-16$\\
\hline
$R^{2}$      &     $0.9978$    &  $0.9985$ & $0.9981$  \\
\hline
\end{tabular}
\caption{\umberto{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a \textbf{faculae}, according to Eq.~\ref{eq:RV:correction}. All the variables, except the intercept when the independent variable is SN median RV, are statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}}
\label{table:faculae.test}
\end{table}

@@

As before, we corrected the originally RV's by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction}. Also in this case the proposed correction almost completely addresses the issue when considering the SN or Normal parameters, with values of $R^2$ larger than 0.99. \xavier{Looking at Fig.~\ref{fig:spot.correction}, we see that the activity correction proposed here is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms. In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however,} \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant. When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.

In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summmurized in Table \ref{table:spot.test}, \umberto{we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF}, are \umberto{not helpful} to understand the variation measured in RV's. This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}. We see also that the ampltitude parameter, with coefficient $\beta_1$ is only useful to explain the RV variation of the spot in the case of the Normal distribution.}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{\umberto{Set of  spurious variations in RV's caused by a \textbf{spot} using a Normal and a SN fit before and once corrected from stellar activity. The new correction has done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity using the proposed linear function (black dots), the residuals present a smaller systematic component if compared with the residuals obtained with the usual correction (blue triangles).}}
    \label{fig:spot.correction}
\end{center}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.4975$    & $0.21$ & $0.21$ \\
\hline
$\beta_{1}$            &    $2e-16$    & $2e-16$ & $2e-16$ \\
\hline
$\beta_{2}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
$\beta_{3}$            &     $0.017$   &  $0.13$ & $0.11$\\
\hline
$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
$R^{2}$      &     $0.9959$    &  $0.9936$ & $0.9952$  \\
\hline
\end{tabular}
\caption{\umberto{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\ref{eq:RV:correction}. All the covariates are statistically useful to explain the variability in RV's caused by a spot, except the intercept and the width of the CCF. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}}
\label{table:spot.test}
\end{table}

@@

%HD192310
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}192310$. The last three plots show the correlation between the FWHM and the RV's for $\text{HD}192310$ using respectively the SN and the Normal fits. The p--values associated with each $R$ is statistically different from $0$.}
   \label{fig:Gliese785:corrPlot}
\end{center}
\end{figure*}

\begin{figure*} 
\begin{center}
\includegraphics[height = 6in]{NEW_CORRECTIONHD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of RV's for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq. \ref{eq:RV:correction}. Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
   \label{fig:HD192310:correctionRV}
\end{center}
\end{figure*}

%HD10700
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}10700$. The last three plots show the correlation between the FWHM and the RV's for $\text{HD}10700$ using respectively the SN and the Normal fits. The p--values associated with each $R$ is statistically different from $0$.}
   \label{fig:Tau:corrPlot}
\end{center}
\end{figure*}

\begin{figure*} 
\begin{center}
\includegraphics[height = 6in]{NEW_CORRECTIONHD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of RV's for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq. \ref{eq:RV:correction}. Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
   \label{fig:HD10700:correctionRV}
\end{center}
\end{figure*}

%HD215152
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}215152$. The last three plots show the correlation between the FWHM and the RV's for $\text{HD}215152$ using respectively the SN and the Normal fits. Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
   \label{fig:HD215152:corrPlot}
\end{center}
\end{figure*}

\begin{figure*} 
\begin{center}
\includegraphics[height = 6in]{NEW_CORRECTIONHD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of RV's for $\text{HD}215152$ using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq. \ref{eq:RV:correction}. Once corrected for stellar activity, the residuals for the Normal are $0.054$ \ms higher than the residuals retrieved with the SN analysis.}
   \label{fig:HD215152:correctionRV}
\end{center}
\end{figure*}

%Corot-7
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
   \caption{Correlation between the asymmetry parameters and the RV's for  $\text{Corot }7$. The last three plots show the correlation between the FWHM and the RV's for  $\text{Corot }7$ using respectively the SN and the Normal fits. Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
   \label{fig:Corot7:corrPlot}
\end{center}
\end{figure*}

\begin{figure*} 
\begin{center}
\includegraphics[height = 6in]{NEW_CORRECTIONLRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of RV's for  $\text{Corot }7$ using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq. \ref{eq:RV:correction}. Once corrected for stellar activity, the residuals for the Normal are $0.336$ \ms higher than the residuals retrieved with the SN analysis.}
   \label{fig:Corot-7:correctionRV}
\end{center}
\end{figure*}
